\pkg{casebase}: An Alternative Framework For Survival Analysis and Comparison of Event Rates

### 2020-09-22 analysis/paper/paper.Rmd
arxiv needs source files. this branch is only for arxiv submission

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  cache = TRUE, 
  fig.pos = 'ht',
  comment = "#>",
  fig.path = "../figures/",
  out.width = "\\textwidth",
   out.extra = "keepaspectratio=true"
)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  cache = TRUE, 
  fig.pos = 'ht',
  comment = "#>",
  # fig.path = "../figures/",
  out.width = "\\textwidth",
   out.extra = "keepaspectratio=true"
)

### 2020-09-22 analysis/paper/paper.tex
arxiv needs source files. this branch is only for arxiv submission

{\centering \includegraphics[width=\textwidth,keepaspectratio=true]{../figures/plot-stratified-erspc-data-1}

@@

\begin{CodeChunk}
\begin{figure}[ht]
\includegraphics[width=\textwidth,keepaspectratio=true]{../figures/erspc-cox-cif-1} \caption{CIFs for control and screening groups in the ERSPC data. In each of the panels, we plot the CIF from the Cox model using \code{survival::survfit} (solid line) and the CIF from the case-base sampling scheme (dashed line) with different functional forms of time. (1) The time variable is excluded (exponential). (2) Linear function of time (Gompertz). (3) The natural logarithm (Weibull). (4) Cubic B-spline expansion of time.}\label{fig:erspc-cox-cif}
\end{figure}
\end{CodeChunk}

@@

{\centering \includegraphics[width=\textwidth,keepaspectratio=true]{../figures/interaction-ERSPC-1}

@@

{\centering \includegraphics[width=\textwidth,keepaspectratio=true]{../figures/compPop-1}

@@

{\centering \includegraphics[width=\textwidth,keepaspectratio=true]{../figures/bmtcrr-risk-1}

@@

{\centering \includegraphics[width=\textwidth,keepaspectratio=true]{../figures/coefplots-1}

@@

{\centering \includegraphics[width=\textwidth,keepaspectratio=true]{../figures/riskregressionBrier-1}

@@

{\centering \includegraphics[width=\textwidth,keepaspectratio=true]{../figures/stanford-poptime-1}

@@

{\centering \includegraphics[width=\textwidth,keepaspectratio=true]{../figures/stanford-hazard-1}

@@

{\centering \includegraphics[width=\textwidth,keepaspectratio=true]{../figures/stanford-risk-1}

>>>>

{\centering \includegraphics[width=\textwidth,keepaspectratio=true]{plot-stratified-erspc-data-1}

@@

\begin{CodeChunk}
\begin{figure}[ht]
\includegraphics[width=\textwidth,keepaspectratio=true]{erspc-cox-cif-1} \caption{CIFs for control and screening groups in the ERSPC data. In each of the panels, we plot the CIF from the Cox model using \code{survival::survfit} (solid line) and the CIF from the case-base sampling scheme (dashed line) with different functional forms of time. (1) The time variable is excluded (exponential). (2) Linear function of time (Gompertz). (3) The natural logarithm (Weibull). (4) Cubic B-spline expansion of time.}\label{fig:erspc-cox-cif}
\end{figure}
\end{CodeChunk}

@@

{\centering \includegraphics[width=\textwidth,keepaspectratio=true]{interaction-ERSPC-1}

@@

{\centering \includegraphics[width=\textwidth,keepaspectratio=true]{compPop-1}

@@

{\centering \includegraphics[width=\textwidth,keepaspectratio=true]{bmtcrr-risk-1}

@@

{\centering \includegraphics[width=\textwidth,keepaspectratio=true]{coefplots-1}

@@

{\centering \includegraphics[width=\textwidth,keepaspectratio=true]{riskregressionBrier-1}

@@

{\centering \includegraphics[width=\textwidth,keepaspectratio=true]{stanford-poptime-1}

@@

{\centering \includegraphics[width=\textwidth,keepaspectratio=true]{stanford-hazard-1}

@@

{\centering \includegraphics[width=\textwidth,keepaspectratio=true]{stanford-risk-1}
